### 2015-05-14 related.tex
Tweaks.

Prior works on static race checking include: \cite{choi2002efficient}, which combined static analysis, optimized instrumentation and runtime access caching to speedup dynamic data race detection; \cite{kahlon2007fast}, which combined a divide-and-conquer strategy that partitions all pointers of a program that cannot alias in disjoint sets and function summarization to achieve a scalable context-sensitive alias analysis for data races; \cite{kahlon2009semantic}, which used abstract interpretation to achieve a sound partial-order reduction on the set of thread interleavings and statically reduce the number of false data race warnings; and \cite{das2015section}, which combined inter-procedural pointer analysis with verifiable user annotations to split programs into disjoint sections, based on non-communicating accesses of shared data, and eliminate redundant checks during dynamic race detection.

>>>>

Prior works on static race checking include: \cite{choi2002efficient}, which combines static analysis, optimized instrumentation and runtime access caching to speedup dynamic data race detection; \cite{kahlon2007fast}, which combines a divide-and-conquer strategy that partitions all pointers of a program that cannot alias in disjoint sets and function summarization to achieve a scalable context-sensitive alias analysis for data races; \cite{kahlon2009semantic}, which uses abstract interpretation to achieve a sound partial-order reduction on the set of thread interleavings and statically reduce the number of false data race warnings; and \cite{das2015section}, which combines inter-procedural pointer analysis with verifiable user annotations to split programs into disjoint sections, based on non-communicating accesses of shared data, and eliminate redundant checks during dynamic race detection.
